Local to global N input modelling

### 2025-05-16 08_manuscript/08_manuscript.qmd
Mean temperature display options

```{r fig-farm-mean-temps}
#| fig-caption: Colours show farm site mean temperature

worldmap <- ne_countries(scale = "medium", returnclass = "sf")
farms_to_omit <- here() %>% 
  file.path("data", "_general_data", "farm_locations", "atlantic_salmon_farms_to_omit.qs") %>% 
  qread()

farms_w_temp_df <- here() %>% 
  file.path("data", "_general_data", "farm_locations", "atlantic_salmon_locations_w_temps.qs") %>% 
  qread() %>% 
  filter(!farm_id %in% farms_to_omit) %>% 
  mutate(country = as.factor(country),
         species_group = as.factor(species_group),
         data_type = as.factor(data_type),
         data_type_2 = as.factor(data_type_2),
         model_name = as.factor(model_name),
         F_CODE = as.factor(F_CODE),
         day = str_split_i(day, "_", 2) %>% as.integer())

farm_temp_means <- farms_w_temp_df %>% 
  select(iso3c, country, farm_id, temp_c)
farm_temp_means_1 <- farms_w_temp_df %>% 
  filter(day == 1) %>% 
  select(geometry)

farm_temp_means <- farm_temp_means %>% 
  group_by(iso3c, country, farm_id) %>% 
  reframe(temp_c = meanna(temp_c))

farm_temp_means <- cbind(farm_temp_means, farm_temp_means_1)

ggplot(data = worldmap, aes(geometry = geometry)) +
  geom_sf(fill = "white", color = "dimgray") +
  geom_sf(data = farm_temp_means, aes(colour = temp_c), size = 1.5) +
  coord_sf() +
  theme_classic()

  theme_classic() +
  theme(legend.position = "bottom", legend.title = element_blank())
```

>>>>

Mean daily temperatures at the farms globally ranged from  from `r round(min(farm_temp_means$mean_temp), 1)`$^{\circ}$ to `r round(max(farm_temp_means$mean_temp), 1)`$^{\circ}$, with an overall mean of `r round(overall_mean, 1)`$^{\circ}$ ($\pm$ `r round(overall_sd, 1)` SD)

```{r fig-farm-mean-temps}
#| fig-cap: Options for showingf arm site mean temperatures. (Top left) Mean temperature by latitude across countries. (Top right) Distribution of mean temperatures by hemisphere. (Bottom) Global distribution of mean temperatures.
#| fig-height: 6
#| fig-width: 6

worldmap <- ne_countries(scale = "medium", returnclass = "sf")

p1 <- ggplot(data = worldmap, aes(geometry = geometry)) +
  geom_sf(fill = "white", color = "dimgray") +
  geom_sf(data = farm_temp_means, aes(colour = mean_temp), size = 1.5) +
  coord_sf() +
  theme_classic()

p2 <- farm_temp_means %>% 
  ggplot(aes(y = mean_temp, x = abs(lat), colour = country)) +
  geom_point(size = 2.5) +
  scale_colour_brewer(palette = "Set1") +
  labs(x = expression("Absolute latitude ("*degree*")"), y = expression("Mean temperature ("*degree*"C)")) +
  theme_classic() +
  theme(legend.position = "top", legend.title = element_blank())

p3 <- farm_temp_means %>% 
  mutate(hemisphere = case_when(lat < 0 ~ "S", T ~ "N")) %>% 
  ggplot(aes(x = mean_temp, fill = hemisphere)) +
  geom_histogram(position = "identity", colour = "black", alpha = 0.5, binwidth = 0.5) +
  labs(x = expression("Mean temperature ("*degree*"C)"), y = "Frequency") +
  theme_classic() +
  theme(legend.position = "top", legend.title = element_blank())

(p2 + p3) / p1 + plot_layout(heights = c(1, 1.5))
```
